Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-08 paper/paper.tex
better? language

Imagine that we are facing the following dilemma:
\begin{quote}
A customer wearing round sunglasses came to a deli at 1:13pm,
and grabbed a sandwich and a coffee. Later on the same day, a
customer wearing round sunglasses came at 6:09pm and ordered a
dinner.  Was it the same customer?
\end{quote}
In addition to the story above, we know that:
\begin{itemize}
    \item There is an adjacent office quarter, and it takes
        between 5 and 15 minutes on average to walk from an
        office to the deli, where different average times are  for
        different buildings in the quarter.
    \item Depending on traffic lights, the walking time varies by about 2
        minutes.
    \item The lunch break starts at 1:00pm, and the workday ends at 6:00pm.
    \item The waiter's odds that this is the same customer are 2 to 1.
\end{itemize}

@@

In addition to computing the posterior probability that the same
customer visited the deli twice, we may want to know the average
time (or times) to arrive. In Bayesian inference, it is common
to report distributions instead of `most likely' values. We use
query results in retrieved samples to approximate the
distributions, and plot distribution histograms for the same
customer visiting twice (Figure~\ref{fig:dist-same}) and
two different customers (Figure~\ref{fig:dist-diff})

@@

In addition to plotting the distribution histograms, we use
functions \texttt{mean}, \texttt{std} provided
in the \texttt{anglican.{\linebreak[0]}stat} namespace
along with other
useful statistical functions.
This is another illustration of advantage of tight
integration between Clojure and Anglican --- probabilistic
models are expressed in Anglican. However, processing of data and
results can rely on the full power of Clojure.

>>>>

Imagine that we are facing the following dilemma:
\begin{quote}
A customer wearing round sunglasses came to a deli at 1:13pm,
and grabbed a sandwich and a coffee. Later on the same day, a
customer wearing round sunglasses came at 6:09pm and ordered a
dinner.  Was it the same customer?
\end{quote}
Additionally, we know that:
\begin{itemize}
    \item There is an adjacent office quarter, and it takes
        between 5 and 15 minutes on average to walk from an
        office to the deli, where different average times are  for
        different buildings in the quarter.
    \item Depending on traffic lights, the walking time varies by about 2
        minutes.
    \item The lunch break starts at 1:00pm, and the workday ends at 6:00pm.
    \item The waiter's odds that this is the same customer are 2 to 1.
\end{itemize}

@@

Besides computing the posterior probability that the same
customer visited the deli twice, we may want to know the average
time (or times) to arrive. In Bayesian inference, it is common
to report distributions instead of `most likely' values. We use
query results in retrieved samples to approximate the
distributions, and plot distribution histograms for the same
customer visiting twice (Figure~\ref{fig:dist-same}) and
two different customers (Figure~\ref{fig:dist-diff})

@@

In addition to plotting the distribution histograms, we use
functions \texttt{mean}, \texttt{std} provided
in the \texttt{anglican.{\linebreak[0]}stat} namespace
along with other useful statistical functions to compute
summary statistics. This is another illustration of advantage of
tight integration between Clojure and Anglican --- probabilistic
models are expressed in Anglican. However, processing of data
and results can rely on the full power of Clojure.
